Semantic Authoring in a Flexiformal Context --- Bulk Annotation of Rigorous Documents

### 2025-07-24 doc/cicm25-paper/paper.tex
minor edits

\documentclass[runningheads]{llncs}
\usepackage[show]{ed}
\usepackage{wrapfig}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{stex-logo}
\usepackage{paralist}
\usepackage[hidelinks]{hyperref}
\usepackage{orcidlink}
%\usepackage{lststex} debug that the gray is not solid
\usepackage{listings}
\definecolor{codegray}{rgb}{0.9,0.9,0.9}
\lstset{basicstyle=\sf,columns=fullflexible,backgroundcolor = \color{codegray}}
\lstset{numberstyle=\tiny}
\lstset{language={[LaTeX]TeX}}
\usepackage[style=alphabetic,hyperref=auto,defernumbers=true,backend=bibtex,firstinits=true,maxbibnames=9,maxcitenames=3,isbn=false]{biblatex}
\addbibresource{kwarcpubs.bib}
\addbibresource{extpubs.bib}
\addbibresource{kwarccrossrefs.bib}
\addbibresource{extcrossrefs.bib}
\usepackage[noabbrev]{cleveref}
\usepackage{tikz}
\usetikzlibrary{shapes}
\usetikzlibrary{arrows}
\usetikzlibrary{docicon}
\usepackage{soul}
\def\edited#1{\hl{#1}}

@@

% To cope with this situation, we are working on extending the brand-new \flams system
% \cite{flams:on}\footnote{A paper on \flams is submitted to CICM 2025 and will be cited
%   here if accepted.} with functionality for handling definienda in the FTML2RDF harvester,
% so that all symbol/verbalizations are available in the \flams triple-store. Thus a harvest
% from the flexiformal content commons would be just a simple SPARQL query and some
% postprocessing of the result (de-duplication, stemming, and pairing) away.
\edited{To cope with this situation, we are planning to extend the brand-new} \flams \edited{system, which among other things powers} \url{https://MathHub.info},
\edited{so that it provides the data necessary to create a
symbol/verbalization catalog.}
Note that
\flams works directly on \FTML, which is generated from \sTeX input by \textsf{rus\TeX}
and exported from annotated MS Word files via \WOIDE~\cite{KohKoh:woide24}. There are two
more systems that could profit from this: The CPoint system that allows annotating MS
PowerPoint presentations with the \sTeX ontology and can already generate a precursor of
\FTML \cite{Kohlhase:SemanticInteractionDesignDiss:biblatex}, and a semantic extension of
Markdown we are developing as a lightweight alternative to \sTeX; it also transforms into
\FTML instead of plain HTML.

@@

In local/private archives, the \snify harvester needs to work directly on the \sTeX
sources.
Currently, \snify uses a custom Python implementation for harvesting the verbalization cache,
but we are working on a implementation based on the new \textbf{\flams linter} -- a simple \sTeX parser that
drives the LSP functionality of the \sTeX IDE plugins for \textsf{VSCode} and \textsf{emacs}.
The analog for this on the \WOIDE side is still under development; it
could be based on \FTML generated by \WOIDE, or \WOIDE could directly export symbol/verbalization
pairs into the \snify verbalization cache.

>>>>

\documentclass[runningheads]{llncs}
\usepackage[show]{ed}
\usepackage{wrapfig}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{stex-logo}
\usepackage{paralist}
\usepackage[hidelinks]{hyperref}
\usepackage{orcidlink}
%\usepackage{lststex} debug that the gray is not solid
\usepackage{listings}
\definecolor{codegray}{rgb}{0.9,0.9,0.9}
\lstset{basicstyle=\sf,columns=fullflexible,backgroundcolor = \color{codegray}}
\lstset{numberstyle=\tiny}
\lstset{language={[LaTeX]TeX}}
\usepackage[style=alphabetic,hyperref=auto,defernumbers=true,backend=bibtex,firstinits=true,maxbibnames=9,maxcitenames=3,isbn=false]{biblatex}
\addbibresource{kwarcpubs.bib}
\addbibresource{extpubs.bib}
\addbibresource{kwarccrossrefs.bib}
\addbibresource{extcrossrefs.bib}
\addbibresource{otherrefs.bib}
\usepackage[noabbrev]{cleveref}
\usepackage{tikz}
\usetikzlibrary{shapes}
\usetikzlibrary{arrows}
\usetikzlibrary{docicon}
\usepackage{soul}
\def\edited#1{\hl{#1}}

@@

% To cope with this situation, we are working on extending the brand-new \flams system
% \cite{flams:on}\footnote{A paper on \flams is submitted to CICM 2025 and will be cited
%   here if accepted.} with functionality for handling definienda in the FTML2RDF harvester,
% so that all symbol/verbalizations are available in the \flams triple-store. Thus a harvest
% from the flexiformal content commons would be just a simple SPARQL query and some
% postprocessing of the result (de-duplication, stemming, and pairing) away.
\edited{To cope with this situation, we are planning to extend the brand-new} \flams
system~\cite{flamsongithub}, \edited{which, among other things, powers} \url{https://MathHub.info},
\edited{so that it provides the data necessary to create a
symbol/verbalization catalog.}
Note that
\flams works directly on \FTML, which is generated from \sTeX input by \textsf{rus\TeX}
and exported from annotated MS Word files via \WOIDE~\cite{KohKoh:woide24}. There are two
more systems that could profit from this: The CPoint system that allows annotating MS
PowerPoint presentations with the \sTeX ontology and can already generate a precursor of
\FTML \cite{Kohlhase:SemanticInteractionDesignDiss:biblatex}, and a semantic extension of
Markdown we are developing as a lightweight alternative to \sTeX; it also transforms into
\FTML instead of plain HTML.

@@

In local/private archives, the \snify harvester needs to work directly on the \sTeX
sources.
Currently, \snify uses a custom Python implementation for harvesting the verbalization cache,
but \edited{we are in the late stages of developing a new} \snify version using the
\textbf{\flams linter} -- a simple \sTeX parser that
drives the LSP functionality of the \sTeX IDE plugins for \textsf{VSCode} and \textsf{emacs}.
The analog for this on the \WOIDE side is still under development; it
could be based on \FTML generated by \WOIDE, or \WOIDE could directly export symbol/verbalization
pairs into the \snify verbalization cache.
